---
title: "LMwithPrediction"
author: "Mariah Kee"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction  
$H_0$ The null hypothesis is that there is no difference in these models, either one is better than the other. 
SH_A$ The alternative hypothesis is that there is a difference in these models and one is better than the other
this is the linear model with prediction problem.
Predict strength scores using data from the following website

```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
```
###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```



```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
new=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,new,interval="prediction")
```

```{r}
plot(SIMS~GRIP,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict.lm(model.2,new,interval="prediction")
```


```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict.lm(model.3,new,interval="prediction")
```
##Compare the 2 models note adjR^2 is larger Residual SE is smaller in model.2

```{r}
anova(model.1,model.3)
```


## Conclusion

Based on the p value of 0.00000499 this is less than 0.05, so we reject the null hypothesis and conclude that model 3 is better than model 1 because it had the larger r square.



